---
title: "Glioma Abstract Analysis"
output: html_notebook
---

## Glioma Analysis

Your task? Investigate changes in glioma-related abstracts from PubMed between 2005 and 2009.



## Load your data by running script

```{r}
glioma_2005 <- readRDS("https://github.com/neonseri/presentationrepo/blob/master/glioma_2005.rds?raw=true")
glioma_2009 <- readRDS("https://github.com/neonseri/presentationrepo/blob/master/glioma_2009.rds?raw=true")
```


## Inspect data 

Text data is inherently messy.  Run the code below to examine the basic structure of the data by printing only the first row of data.

```{r}
head(glioma_2005, 1)
```

```{r}
head(glioma_2009, 1)
```


## How many rows of data do you have?  Use nrow()


```{r}
nrow(glioma_2005, 1)
```

```{r}
nrow(???, 1)
```


## Investigating mentions of `stem cell` using grepl() for 2005

grepl returns TRUE/FALSE statements if patterns of interest appear. 

```{r}
glioma_2005$stemcell <- grepl("stem cell", glioma_2005$text, ignore.case = TRUE)
head(glioma_2005$stemcell, 5)
```

One way to count number of stem cell glioma articles is by summing up the TRUE and FALSE. TRUE gets treated as 1, FALSE gets treated as 0 by the sum() function.  How many articles mentioned stem cell?

```{r}
sum(glioma_2005$stemcell)
```

## Performing the previous task for 2009

```{r}
???
```



```{r}
???
```



## Quick Stop

Did you notice anything interesting about stem cell mentions in 2005 vs 2009?




## Feel free to investigate other trends you may want to check.




## Other things you might want to check


If you are interested in exploring a popular package called tidytext, let us work on it in this section (feel free to call me).





